Learning Features and Abstract Actions for Computing Generalized Plans

### 2018-11-13 doc/camera-ready/paper.tex
Changes in discussion + summary

The \emph{complexity} of a concept or role is the minimum number of grammar  rules needed to generate it.
The set of concepts and roles with complexity no greater than  $k$ is referred to as  $\G^k$.
When generating  $\G^k$,  redundant  concepts are incrementally pruned. A concept is deemed
redundant when its  denotation coincides with the denotation of a previously generated concept 
over all  states in $\S$.  The set $\F=\F^k$, defined from $\G^k$, contains the following features:
\begin{enumerate}[{\small$\bullet$}]
  \item For each nullary primitive predicate $p$, a \emph{boolean}
    feature $b_p$ that is true in $s$ iff $p$ is true in $s$.
  %
  \item For each concept $C$, a \emph{boolean} feature $b_C$, if
    $|C^s| \in \set{0,1}$ for all sampled states $s$, and a \emph{numerical}
    feature $n_C$ otherwise. The value of $b_C$ in $s$ is true iff $|C^s| > 0$;
    the value of $n_C$ is $|C^s|$.
  %
  \item Numerical features $\textit{dist}(C_1,R{:}C,C_2)$ that represent the
    smallest $n$ such that there are objects $x_1, \ldots, x_n$ satisfying
    $C_1^s(x_1)$, $C_2^s(x_{n})$, and $(R{:}C)^s(x_i,x_{i+1})$ for $i=1,\ldots,n$.
    The denotation $(R{:}C)^s$ contains all pairs $(x,y)$ in $R^s$ such that $y\in C^s$.
\end{enumerate}

@@

A second limitation is the assumption that 
the features can be obtained from a large pool of candidate  features defined 
from the primitive predicates and a  general grammar.
It is not fully clear whether this assumption is reasonable in general.
A relevant argument made by \citeay{bonet:ijcai2018} is that generalized problems
over domains with low width \cite{nir:ecai2012}, have compact policies
in terms of general features that can be computed in polynomial time.
In addition, for dealing with arbitrary goals, the same grammar  appears
to be suitable, once  \emph{goal predicates}, namely, copies $p_G$ of the  primitive predicates $p$
that appear in the goal,  are added to the set of primitive predicates and are evaluated in the goal
\cite{martin-geffner:generalized}.

@@

Finally, problems involving non-deterministic transitions may be
accounted for with a simple change to the SAT theory.
It would be sufficient to replace the formula \eqref{eq:bridge1}
that links $D1$ and $D2$ with a formula that establish that when
$s$ and $t$ are indistinguishable (i.e.\ $\neg D1(s,t)$), then
for each action $a$ on $s$, there is an action $b$ on $t$ whose
set of transitions from $t$ are indistinguishable from the set
of transitions of $a$ on $s$.
To do this, transitions $(s,s')$ in the sample would need to be
tagged with action labels as $(s,a,s')$.

>>>>

The \emph{complexity} of a concept or role is the minimum number of grammar  rules needed to generate it.
The set of concepts and roles with complexity no greater than  $k$ is referred to as  $\G^k$.
When generating  $\G^k$,  redundant  concepts are incrementally pruned. A concept is deemed
redundant when its  denotation coincides with the denotation of a previously generated concept 
over all  states in $\S$.  The set $\F=\F^k$, defined from $\G^k$, contains the following features:
\begin{enumerate}[{\small$\bullet$}]
  \item For each nullary primitive predicate $p$, a \emph{boolean}
    feature $b_p$ that is true in $s$ iff $p$ is true in $s$.
  %
  %\item For each concept $C$, a \emph{boolean} feature $b_C$, if $|C^s|\leq 1$
  \item For each concept $C$, a \emph{boolean} feature $b_C$, if $|C^s| \in \set{0,1}$
    for all sampled states $s$, and a \emph{numerical} feature $n_C$ otherwise.
    The value of $b_C$ in $s$ is true iff $|C^s| > 0$; the value of $n_C$ is $|C^s|$.
  %
  \item Numerical features $\textit{dist}(C_1,R{:}C,C_2)$ that represent the
    smallest $n$ such that there are objects $x_1, \ldots, x_n$ satisfying
    $C_1^s(x_1)$, $C_2^s(x_{n})$, and $(R{:}C)^s(x_i,x_{i+1})$ for $i=1,\ldots,n$.
    The denotation $(R{:}C)^s$ contains all pairs $(x,y)$ in $R^s$ such that $y\in C^s$.
\end{enumerate}

@@

It is not fully clear whether it is reasonable in general
to assume that the features can be obtained from a large
pool of candidate features that is defined from the primitive
predicates and a general concept grammar.
%A second limitation is the assumption that 
%the features can be obtained from a large pool of candidate  features defined 
%from the primitive predicates and a  general grammar.
%It is not fully clear whether this assumption is reasonable in general.
A relevant argument made by \citeay{bonet:ijcai2018} is that generalized problems
over domains with low width \cite{nir:ecai2012}, have compact policies
in terms of general features that can be computed in polynomial time.
In addition, for dealing with arbitrary goals, the same grammar  appears
to be suitable once  \emph{goal predicates}, namely, copies $p_G$ of the primitive predicates $p$
that appear in the goal, are added to the set of primitive predicates and evaluated in the goal
\cite{martin-geffner:generalized}.

Finally, while we have dealt with instances with deterministic actions
only, the formulation can be extended to handle non-deterministic actions.
Indeed, it is sufficient to replace the formula \eqref{eq:bridge1}
that links $D1$ and $D2$ with a formula to establish that when states
$s$ and $t$ are indistinguishable (i.e.\ $\neg D1(s,t)$), then
for each action $a$ for $s$, there is an action $b$ for $t$ whose
set of transitions on $t$ is indistinguishable from the set
of transitions of $a$ on $s$; namely, for each transition $(s,a,s')$
there is a transition $(t,b,t')$ with $\Delta_f(s,s')=\Delta_f(t,t')$
for each feature $f$, and vice versa.
To do this, transitions $(s,s')$ in the sample would need to be
tagged with action labels as $(s,a,s')$.

@@

%Finally, problems involving non-deterministic transitions may be
%accounted for with a simple change to the SAT theory.
%It would be sufficient to replace the formula \eqref{eq:bridge1}
%that links $D1$ and $D2$ with a formula that establishes that when
%$s$ and $t$ are indistinguishable (i.e.\ $\neg D1(s,t)$), then
%for each action $a$ for $s$, there is an action $b$ for $t$ whose
%set of transitions on $t$ is indistinguishable from the set
%of transitions of $a$ on $s$; namely, for each transition $(s,a,s')$
%there is a transition $(t,b,t')$ with $\Delta_f(s,s')=\Delta_f(t,t')$
%for each feature $f$, and vice versa.
%To do this, transitions $(s,s')$ in the sample would need to be
%tagged with action labels as $(s,a,s')$.
